### 2016-09-11 draft/draft.tex
Fix chapter headingFix chapter headings
Fix subsections

\renewcommand{\baselinestretch}{1.5}
\lstset{breaklines=true}

@@

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

@@

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\section{Contents}\label{contents}

\emph{ToC TODO}

@@

\section{Abbreviations}\label{abbreviations}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

@@

\section{Chapter 1}\label{chapter-1}

\section{Introduction}\label{introduction}

\subsection{1.1 Problem Outline}\label{problem-outline}

@@

\subsection{1.2 Project Goals}\label{project-goals}

@@

\subsection{1.3 Personal Aims}\label{personal-aims}

@@

\subsection{1.4 Project Management}\label{project-management}

@@

\subsection{1.5 Report Overview}\label{report-overview}

@@

\section{Chapter 2}\label{chapter-2-1}

\section{Background Information and Related
Applications}\label{background-information-and-related-applications}

\subsection{2.1 Blockchains \& Dropouts}\label{blockchains-dropouts}

@@

\subsection{2.2 Previous Work/Existing
Applications}\label{previous-workexisting-applications}

@@

\subsection{2.3 Programming Languages and
Libraries}\label{programming-languages-and-libraries}

\subsubsection{2.3.1 Blockchain}\label{blockchain}

@@

\subsubsection{2.3.2 Server-side}\label{server-side}

@@

\subsubsection{2.3.3 Client-side}\label{client-side}

@@

\subsubsection{2.3.4 Testing}\label{testing}

@@

\subsubsection{2.3.5 Databases: SQL vs NoSQL vs
Blockchain}\label{databases-sql-vs-nosql-vs-blockchain}

@@

\subsection{2.4 Tooling}\label{tooling}

\subsubsection{2.4.1 Requirements and Design
Tools}\label{requirements-and-design-tools}

@@

\subsubsection{2.4.2 Development Tools}\label{development-tools}

@@

\section{Chapter 3}\label{chapter-3-1}

\section{Requirements and Analysis}\label{requirements-and-analysis}

\subsection{3.1 Problem Statement}\label{problem-statement}

@@

\subsection{3.2 Requirements}\label{requirements}

@@

\subsection{3.3 Use Cases}\label{use-cases}

@@

\subsection{3.4 Sketches}\label{sketches}

@@

\subsection{3.5 System Design}\label{system-design}

@@

\subsubsection{3.5.1 Smart Contract
Analysis}\label{smart-contract-analysis}

@@

\subsubsection{3.5.2 Server-side Analysis}\label{server-side-analysis}

@@

\subsubsection{3.5.3 Client-side Analysis}\label{client-side-analysis}

@@

\section{Chapter 4}\label{chapter-4-1}

\section{Design \& Implementation}\label{design-implementation}

\subsection{4.1 System Architecture}\label{system-architecture}

@@

\subsection{4.2 Blockchain Design \&
Implementation}\label{blockchain-design-implementation}

\subsubsection{4.2.1 The Model}\label{the-model}

@@

\subsubsection{4.2.2 Working with Solidity}\label{working-with-solidity}

@@

\subsubsection{4.2.3 Smart Contracts}\label{smart-contracts}

@@

\subsubsection{4.2.4 Deploying Validator
Nodes}\label{deploying-validator-nodes}

@@

\subsection{4.3 Server Design \&
Implementation}\label{server-design-implementation}

@@

\subsubsection{4.3.1 The Controller}\label{the-controller}

@@

\subsubsection{4.3.2 RESTfulness}\label{restfulness}

@@

\subsection{4.4 Client-side Design \&
Implementation}\label{client-side-design-implementation}

\subsubsection{4.4.1 The View}\label{the-view}

@@

\subsubsection{4.4.2 JavaScript: Emulating Strict
Typing}\label{javascript-emulating-strict-typing}

@@

\subsubsection{4.4.3 React: Common
Components}\label{react-common-components}

@@

\subsubsection{4.4.4 Redux: UI and I/O}\label{redux-ui-and-io}

@@

\section{Chapter 5}\label{chapter-5-1}

\section{Testing}\label{testing-1}

\subsection{5.1 Testing Strategy}\label{testing-strategy}

@@

\subsection{5.2 Unit Testing}\label{unit-testing}

@@

\subsection{5.3 Integration Testing}\label{integration-testing}

@@

\subsection{5.4 Functional Testing}\label{functional-testing}

@@

\subsection{5.5 Coverage}\label{coverage}

@@

\section{Chapter 6}\label{chapter-6-1}

\section{Conclusions and Project
Evaluation}\label{conclusions-and-project-evaluation}

\subsection{6.1 Project Goals}\label{project-goals-1}

@@

\subsection{6.2 Personal Aims Achieved}\label{personal-aims-achieved}

@@

\subsection{6.3 Critical Evaluation}\label{critical-evaluation}

\subsubsection{6.3.1 Scope Feasibility}\label{scope-feasibility}

@@

\subsubsection{6.3.2 Suitability of Chosen
Technologies}\label{suitability-of-chosen-technologies}

@@

\subsection{6.4 Future Work}\label{future-work}

@@

\subsection{6.5 Final Thoughts}\label{final-thoughts}

>>>>

\renewcommand{\baselinestretch}{1.5}
\lstset{breaklines=true}

\usepackage{chngcntr}
\counterwithin{figure}{chapter}

@@

@@

@@

@@

\chapter{Introduction}

\section{1.1 Problem Outline}\label{problem-outline}

@@

\section{1.2 Project Goals}\label{project-goals}

@@

\section{1.3 Personal Aims}\label{personal-aims}

@@

\section{1.4 Project Management}\label{project-management}

@@

\section{1.5 Report Overview}\label{report-overview}

@@

\chapter{Background Information and Related
Applications}

\section{2.1 Blockchains \& Dropouts}\label{blockchains-dropouts}

@@

\section{2.2 Previous Work/Existing
Applications}\label{previous-workexisting-applications}

@@

\section{2.3 Programming Languages and
Libraries}\label{programming-languages-and-libraries}

\subsection{2.3.1 Blockchain}\label{blockchain}

@@

\subsection{2.3.2 Server-side}\label{server-side}

@@

\subsection{2.3.3 Client-side}\label{client-side}

@@

\subsection{2.3.4 Testing}\label{testing}

@@

\subsection{2.3.5 Databases: SQL vs NoSQL vs
Blockchain}\label{databases-sql-vs-nosql-vs-blockchain}

@@

\section{2.4 Tooling}\label{tooling}

\subsection{2.4.1 Requirements and Design
Tools}\label{requirements-and-design-tools}

@@

\subsection{2.4.2 Development Tools}\label{development-tools}

@@

\chapter{Requirements and Analysis}

\section{3.1 Problem Statement}\label{problem-statement}

@@

\section{3.2 Requirements}\label{requirements}

@@

\section{3.3 Use Cases}\label{use-cases}

@@

\section{3.4 Sketches}\label{sketches}

@@

\section{3.5 System Design}\label{system-design}

@@

\subsection{3.5.1 Smart Contract
Analysis}\label{smart-contract-analysis}

@@

\subsection{3.5.2 Server-side Analysis}\label{server-side-analysis}

@@

\subsection{3.5.3 Client-side Analysis}\label{client-side-analysis}

@@

\chapter{Design \& Implementation}

\section{4.1 System Architecture}\label{system-architecture}

@@

\section{4.2 Blockchain Design \&
Implementation}\label{blockchain-design-implementation}

\subsection{4.2.1 The Model}\label{the-model}

@@

\subsection{4.2.2 Working with Solidity}\label{working-with-solidity}

@@

\subsection{4.2.3 Smart Contracts}\label{smart-contracts}

@@

\subsection{4.2.4 Deploying Validator
Nodes}\label{deploying-validator-nodes}

@@

\section{4.3 Server Design \&
Implementation}\label{server-design-implementation}

@@

\subsection{4.3.1 The Controller}\label{the-controller}

@@

\subsection{4.3.2 RESTfulness}\label{restfulness}

@@

\section{4.4 Client-side Design \&
Implementation}\label{client-side-design-implementation}

\subsection{4.4.1 The View}\label{the-view}

@@

\subsection{4.4.2 JavaScript: Emulating Strict
Typing}\label{javascript-emulating-strict-typing}

@@

\subsection{4.4.3 React: Common
Components}\label{react-common-components}

@@

\subsection{4.4.4 Redux: UI and I/O}\label{redux-ui-and-io}

@@

\chapter{Testing}

\section{5.1 Testing Strategy}\label{testing-strategy}

@@

\section{5.2 Unit Testing}\label{unit-testing}

@@

\section{5.3 Integration Testing}\label{integration-testing}

@@

\section{5.4 Functional Testing}\label{functional-testing}

@@

\section{5.5 Coverage}\label{coverage}

@@

\chapter{Conclusions and Project
Evaluation}

\section{6.1 Project Goals}\label{project-goals-1}

@@

\section{6.2 Personal Aims Achieved}\label{personal-aims-achieved}

@@

\section{6.3 Critical Evaluation}\label{critical-evaluation}

\subsection{6.3.1 Scope Feasibility}\label{scope-feasibility}

@@

\subsection{6.3.2 Suitability of Chosen
Technologies}\label{suitability-of-chosen-technologies}

@@

\section{6.4 Future Work}\label{future-work}

@@

\section{6.5 Final Thoughts}\label{final-thoughts}
